---
title: "Data Import"
output: github_document
---

```{r setup}
library(tidyverse)
```

## Read in some data

Read in the litters dataset.

```{r}
litters_df = read_csv("./FAS_litters.csv") # "."=starts here
litters_df = janitor::clean_names(litters_df)
```


## Take a look at the data

Printing in the console.
```{r}
litters_df
```

```{r}
tail(litters_df)
```

```{r}
skimr::skim(litters_df)
```


view(litters_df) # use this more often


## Options to read csv

```{r}
litters_df = read_csv("./FAS_litters.csv", skip = 10, col_names = F)
```

litters_df = read_csv("./FAS_litters.csv", skip = 10, col_names = F, na = c("", "NA", 999, "")) # see if there are missing values like this

check out '?read_csv()' for some information.

## Other file format

Read in excel file.

```{r}
library(readxl) # put it in the top
mlb_df = read_excel("./mlb11.xlsx", range = "A1:F7")
mlb_df
```

Read in a SAS file.

```{r}
library(haven)
pulse_df = read_sas("./public_pulse_data.sas7bdat")
```
# dbl is treated as numbers


## Comparison with Base R

what about `read.csv` ...? Never use it, use_

```{r}
litters_base = read.csv("FAS_litters.csv") # more difficult to look at
litters_readr = read_csv("FAS_litters.csv")

litters_base
litters_readr
```

